Applying the metallicity-dependent binary fraction to double white dwarf formation: \\ Implications for LISA

### 2022-11-18 src/tex/ms.tex

Figure~\ref{fig:Mc_vs_dist_vars} shows the chirp mass vs. distance distribution for the $\alpha25$, $\alpha5$, and $q3$ parameter variations. For $\alpha25$ we plot scatter plots for He + He and ONe + X due to low statistics; there are too few binaries in this selected population to produce reliable kernel density estimates. The only population with a significant change between \textbf{binary fraction models} is for ONe + X DWDs\textbf{, variation} $\alpha5$. Here, we find a skew to lower \textbf{chirp} masses because a higher fraction of the binaries are ONe + He for FZ \textbf{compared to} F50: a Helium companion makes up 44\% of this selected population for FZ, compared with 10\% for F50. This leads to lower average chirp masses for the ONe + X distribution. Furthermore, $\sim8$\% of the F50 measurable systems are ONe + ONe binaries, versus 0\% for FZ. Because ONe WDs have larger masses, this also creates the high-mass concentration we \textbf{find} in the F50 contours.
\begin{figure*}[h]
    \centering
	\includegraphics[width=0.8\textwidth]{figures/Mc_vs_dist_alpha25.pdf}
	\includegraphics[width=0.8\textwidth]{figures/Mc_vs_dist_alpha5.pdf}
	\includegraphics[width=0.8\textwidth]{figures/Mc_vs_dist_q3.pdf}
    \caption{Chirp mass -- distance distributions for our other three binary evolution parameter variations. We plot the $\alpha25$ populations of He + He and ONe + X DWDs as scatter points since there are too few binaries to produce meaningful density distributions. Again, we have plotted each DWD type's population that exhibit observable GW frequency evolution and have $\rm{SNR}>7$. Contours show the 5$^{\rm{th}}$, 25$^{\rm{th}}$, 50$^{\rm{th}}$, 75$^{\rm{th}}$ and 95$^{\rm{th}}$ percentiles. Most populations remain unchanged between binary fraction models except for ONe + X DWDs in $\alpha5$, due to the number of He vs. CO vs. ONe companions between each model.}
    \label{fig:Mc_vs_dist_vars}
    \script{Mc_vs_dist.py}
\end{figure*}
\end{document}

>>>>

Figure~\ref{fig:Mc_vs_dist_vars} shows the chirp mass vs. distance distribution for the $\alpha25$, $\alpha5$, and $q3$ parameter variations. For $\alpha25$ we plot scatter plots for He + He and ONe + X due to low statistics; there are too few binaries in this selected population to produce reliable kernel density estimates. The only population with a significant change between \textbf{binary fraction models} is for ONe + X DWDs\textbf{, variation} $\alpha5$. Here, we find a skew to lower \textbf{chirp} masses because a higher fraction of the binaries are ONe + He for FZ \textbf{compared to} F50: a Helium companion makes up \textbf{38\%} of this selected population for FZ, compared with \textbf{12\%} for F50. This leads to lower average chirp masses for the ONe + X distribution. Furthermore, \textbf{$\sim6$\%} of the F50 measurable systems are ONe + ONe binaries, versus 0\% for FZ. Because ONe WDs have larger masses, this also creates the high-mass concentration we \textbf{find} in the F50 contours.
\begin{figure*}[h]
    \centering
	\includegraphics[width=0.8\textwidth]{figures/Mc_vs_dist_alpha25.pdf}
	\includegraphics[width=0.8\textwidth]{figures/Mc_vs_dist_alpha5.pdf}
	\includegraphics[width=0.8\textwidth]{figures/Mc_vs_dist_q3.pdf}
    \caption{Chirp mass -- distance distributions for our other three binary evolution parameter variations. We plot the $\alpha25$ populations of He + He and ONe + X DWDs as scatter points since there are too few binaries to produce meaningful density distributions. Again, we have plotted each DWD type's population that exhibit observable GW frequency evolution and have $\rm{SNR}>7$. Contours show the 5$^{\rm{th}}$, 25$^{\rm{th}}$, 50$^{\rm{th}}$, 75$^{\rm{th}}$ and 95$^{\rm{th}}$ percentiles. Most populations remain unchanged between binary fraction models except for ONe + X DWDs in $\alpha5$, due to the number of He vs. CO vs. ONe companions between each model.}
    \label{fig:Mc_vs_dist_vars}
    \script{Mc_vs_dist.py}
\end{figure*}
\end{document}
